TITLE

### 2017-09-25 paper/paper.tex
add subsection for LSTM

@@

@@

@@

@@

@@

>>>>

Our own Model consisted of the Decoder of a trained Autoencoder for the pretrained images and a Long short-Term memory\cite{LSTM} network that classifies these representations of the Decoder. \textbf{DOES ANYBODY HAVE A GRAPHIC OF OUR WHOLE ARCHITECTURE?}

@@

\subsection{Bidirectional LSTM}
For our classification we used several layers of LSTMs, because the temporal dependencies of our data are little understood. We wanted to allow the model to classify according to anomalies or structure of the sequence. Unidirectional and bidirectional LSTMs were tried, the latter ones learn much faster and more. This is probably due to uncertainty where in the sequence the rich part of the data is, unlikelihood that is at similar positions and the fact that the data is not temporally resolving but just developing so it can be viewed equally from both directions. Several number of layers and dropout rates were tried, $2$ layers and a $0.1$ dropout scored highest. These relatively small numbers could both be due to the small dataset. A little improvement was gained by replacing hard-sigmoid activation for the input with sigmoid activation. All models were trained for $50$ epochs over the whole training set. The models were first trained without the weights of the decoder and then compared to the model with trained decoder.

@@

We used 8-fold validation for our results.
\subsubsection{Baseline Models}

@@

\subsubsection{LSTMs without trained decoder}
 2 layer unidirectional LSTM & - & 18.55\% $\pm \% $\\ 
 2 layer bidirectional LSTM & - & 83.68\% $\pm \%$ \\ 
 3 layer bidirectional LSTM & - & 83.39\% $\pm \%$ \\ 
 5 layer bidirectional LSTM & - & 75.78\% $\pm \%$ \\
 2 layer bidirectional LSTM with 0.1 dropout & - & 84.08\% $\pm \%$ \\
 2 layer bidirectional LSTM with 0.2 dropout & - & 79.87\% $\pm \%$ \\
\subsubsection{LSTMs with trained decoder}
 2 layer bidirectional LSTM with 0.2 dropout & - & 89.21\% $\pm \%$ \\

@@

	\bibitem{LSTM}
	Hochreiter, Sepp and Schmidhuber, Jürgen (1997).
	\textit{Long Short-term Memory}
	In Neural Computation 9:1735-80

@@

    © 2017 GitHub, Inc.
    Terms
    Privacy
    Security
    Status
    Help

    Contact GitHub
    API
    Training
    Shop
    Blog
    About
